\documentclass[12pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{array}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{tocloft}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{multirow}
\usepackage{footmisc}
\usepackage{csquotes}
\usepackage{pdfpages}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue,
  citecolor=blue
}

% Formatting
\onehalfspacing
\setlength{\parskip}{0.6em}
\setlength{\parindent}{0pt}
\titlespacing*{\section}{0pt}{1.2em}{0.4em}
\titlespacing*{\subsection}{0pt}{1.0em}{0.3em}
\titlespacing*{\subsubsection}{0pt}{0.8em}{0.2em}

% Header/Footer
\pagestyle{fancy}
\fancyhf{}
\lhead{JOBEASE Synopsis}
\rhead{\thepage}

% Table of contents spacing
\setlength{\cftbeforetoctitleskip}{-0.5em}
\setlength{\cftaftertoctitleskip}{1em}

% Code style
\lstdefinestyle{code}{
  basicstyle=\ttfamily\small,
  breaklines=true,
  frame=single,
  backgroundcolor=\color{black!2},
  keywordstyle=\color{blue},
  commentstyle=\color{gray!70},
  stringstyle=\color{green!40!black},
  numbers=left,
  numberstyle=\tiny, numbersep=6pt
}

\begin{document}

\begin{titlepage}
  \centering
  {\Large\bfseries JOBEASE: Intelligent Career Matching and Application Automation\\[0.6em]}
  {\large Comprehensive Project Synopsis (A4, ~30 pages)}\\[2em]
  {\large Date: \today}\\[8em]
  \vfill
  \textit{Abstract}\\[0.8em]
  JobEase is an AI-powered platform that streamlines the end-to-end job search lifecycle for candidates and improves applicant quality for employers. The platform leverages natural language processing (NLP), retrieval augmented generation (RAG), structured skills ontologies, and workflow automation to provide: (1) personalized job discovery, (2) ATS-optimized resume tailoring, (3) role-specific cover letters and screening responses, (4) autofill of application forms, (5) a unified application tracker, and (6) analytics for continuous improvement. This synopsis presents the product vision, problem framing, stakeholder analysis, market landscape, solution architecture, data model, ML/NLP techniques, system design (frontend, backend, and DevOps), privacy and compliance posture, risk analysis, project plan, and validation strategy.
  \vfill
\end{titlepage}

\tableofcontents
\newpage

\section{Introduction}
The modern job market is fragmented across platforms, formats, and workflows. Candidates repetitively tailor resumes, compose cover letters, answer screening questions, and submit applications, often with limited feedback loops. Employers are overwhelmed by volume and rely on ATS keyword heuristics that frequently mis-rank qualified candidates. JobEase aims to close this gap with an intelligent, privacy-respecting assistant that automates low-value tasks and elevates the quality of candidate-employer matches.

JobEase is delivered as a cross-platform mobile and desktop experience using Expo and React Native for rapid iteration, consistent UX, and broad reach. This synopsis details how we will realize the product vision from concept to a secure, scalable MVP and beyond.

\subsection{Vision}
To reduce time-to-application by \SI{60}{\percent}--\SI{80}{\percent}, increase interview rate by \(2\text{--}3\times\), and improve employer screening precision via semantically enriched candidate profiles, while safeguarding user privacy.

\subsection{Document Structure}
This document covers problem framing, solution architecture, data and ML components, security and compliance, delivery plan, and validation strategy. It targets practitioners, stakeholders, and evaluators.

\section{Problem Statement and Motivation}
\subsection{Candidate Pain Points}
\begin{itemize}[leftmargin=2em]
  \item Manual tailoring of resumes and cover letters for each role.
  \item Repetitive form filling across disparate application portals.
  \item Limited insight into what improves success probability.
  \item Friction from inconsistent application schemas and ATS keyword filters.
\end{itemize}
\subsection{Employer Pain Points}
\begin{itemize}[leftmargin=2em]
  \item High volume with low signal-to-noise ratios in applications.
  \item Overreliance on keyword heuristics that miss contextual fit.
  \item Time-consuming screening with limited structured data.
\end{itemize}
\subsection{Motivation and Goals}
\begin{itemize}[leftmargin=2em]
  \item Compress the candidate workflow and increase throughput without sacrificing quality.
  \item Provide employers higher-fidelity, structured candidate profiles for better matching.
  \item Embed privacy by design and enable transparent user control of data.
\end{itemize}

\section{Objectives and Success Criteria}
\subsection{Primary Objectives}
\begin{enumerate}[leftmargin=2em]
  \item Personalized job discovery and ranking.
  \item Automated resume tailoring and cover letter generation.
  \item Application autofill and unified tracking.
  \item Privacy-first design with explicit consent and transparency.
  \item Scalable, observable, and maintainable architecture.
\end{enumerate}
\subsection{Key Performance Indicators}
\begin{itemize}[leftmargin=2em]
  \item \textbf{Discovery}: $>\SI{30}{\percent}$ click-through on top-5 recommendations.
  \item \textbf{Tailoring}: $\geq \SI{70}{\percent}$ reduction in manual edits per application.
  \item \textbf{Autofill}: $\geq \SI{50}{\percent}$ of fields populated accurately on first pass.
  \item \textbf{Reliability}: P95 $< \SI{500}{\milli\second}$ for core APIs; $>\SI{99.9}{\percent}$ uptime.
\end{itemize}

\section{Stakeholders and Personas}
\subsection{Candidate Personas}
\begin{description}
  \item[Recent Graduate] Seeks entry roles; needs guidance, portfolio building, and acceleration.
  \item[Mid-Career Switcher] Transitioning domains; needs skills mapping and evidence reframing.
  \item[International Applicant] Requires localization, visa filters, and credential recognition.
\end{description}
\subsection{Employer Personas}
\begin{description}
  \item[Recruiter] Desires stronger shortlists with structured skills evidence.
  \item[Hiring Manager] Seeks interview-ready candidates with scoped experience.
\end{description}

\section{Market Research and Competitive Landscape}
\subsection{Landscape}
Job boards (Indeed, LinkedIn Jobs), ATS platforms (Workday, Greenhouse, Lever), and AI resume tools offer partial solutions. Most lack end-to-end automation and semantically grounded matching.
\subsection{Differentiation}
JobEase integrates discovery, tailoring, autofill, and tracking, backed by a RAG knowledge base, skills ontologies, and a feedback-driven recommendation loop.

\section{Product Scope and Feature Set}
\subsection{MVP Scope}
\begin{itemize}[leftmargin=2em]
  \item Job feed with semantic search and filters.
  \item Resume tailoring: skills alignment, quantified achievements, ATS-friendly formatting.
  \item Cover letter and screening Q\&A generation.
  \item Application autofill with site-specific mappings and OCR fallback.
  \item Application tracker with reminders and status sync.
  \item Insights: gap analysis, skills roadmap, interview prep guidance.
\end{itemize}
\subsection{Non-Goals (MVP)}
Employer-side ATS replacement; enterprise SSO.

\section{User Journeys and UX Flows}
\subsection{Onboarding}
Import resume; parse to profile; confirm skills; connect sources.
\subsection{Discover}
Browse personalized recommendations; save, compare, and filter.
\subsection{Tailor}
One-click resume and cover letter generation with an editable review loop.
\subsection{Apply}
Autofill forms; verify; submit; track status.
\subsection{Track}
Unified tracker; deadlines; notes; reminders; analytics.

\section{System Architecture Overview}
\subsection{Logical Tiers}
\begin{itemize}[leftmargin=2em]
  \item Client apps (Expo/React Native) for iOS/Android/Web.
  \item API gateway and backend services (TypeScript/Node or Python).
  \item NLP/ML services for parsing, matching, and generation.
  \item Data layer: relational DB, vector store, and blob storage.
\end{itemize}
\subsection{Cross-Cutting Concerns}
Observability, privacy, security, configuration, and feature flags.

\section{Domain Model and Data Schema}
\subsection{Core Entities}
User, CandidateProfile, Employer, JobPosting, Application, Document, ResumeVersion, CoverLetter, InteractionEvent, Recommendation, Insight.
\subsection{Relational Schema (Illustrative)}
\begin{longtable}{p{0.24\linewidth} p{0.7\linewidth}}
\toprule
\textbf{Table} & \textbf{Key Fields}\\
\midrule
Users & auth\_id, email, consent\_flags, locale, created\_at\\
CandidateProfile & user\_id (FK), skills JSONB, experience[], education[], certifications[]\\
JobPosting & source, url, title, description, skills\_extracted[], location, salary\_range\\
Application & user\_id, job\_id, status, submitted\_at, tracker\_fields\\
Documents & user\_id, type, storage\_uri, checksum, created\_at\\
\bottomrule
\end{longtable}
\subsection{Vector Indices}
Embeddings for job descriptions and candidate skills enable similarity search and hybrid retrieval.

\section{NLP/ML Components and Models}
\subsection{Parsing}
Layout-aware resume parsing (e.g., LayoutLMv3 or equivalent) for robust extraction of entities and structure.
\subsection{Skill Normalization}
Mapping extracted skills to a curated ontology (ESCO/ONET + custom taxonomy) to standardize synonyms and hierarchies.
\subsection{Embeddings and Similarity}
Sentence-level embeddings enable content-based matching between candidate profiles and jobs.
\subsection{RAG Knowledge Base}
A curated knowledge base of best practices, templates, and phrasing patterns; retrieved via hybrid search (BM25 + vector).
\subsection{Prompt Engineering}
System/instruction/exemplar prompts with constrained JSON outputs to ensure structure and reliability.

\section{Resume Tailoring and Scoring Engine}
\subsection{Inputs}
Base resume, target job, candidate profile.
\subsection{Process}
Extract role requirements; map candidate evidence; quantify impact; rewrite bullets to ATS-friendly structure; enforce length and readability constraints.
\subsection{Outputs}
Tailored resume version with change log and a match score for prioritization.
\subsection{Scoring Features}
Skill overlap, seniority alignment, quantified achievements, keyword coverage, readability, and content length.

\section{Job Ingestion, Parsing, and Normalization}
\subsection{Sources}
Public APIs, RSS, respectful scraping, and user-imported links.
\subsection{Normalization}
Title standardization, location parsing, seniority tagging, skill mapping.
\subsection{Deduplication}
URL canonicalization, content hashing, fuzzy matching to remove duplicates.

\section{Application Autofill and ATS Integrations}
\subsection{Autofill Strategy}
Map profile fields to common application schemas; store site-specific field mappings and validation rules.
\subsection{Delivery Modalities}
Browser automation for desktop portals, deep links where supported on mobile, and secure credential vaulting.
\subsection{Integrations Roadmap}
Greenhouse, Lever, Workday via partner APIs or user-authorized credentials.

\section{RAG Knowledge Base and Prompt Engineering}
\subsection{Content}
Resume best practices, industry templates, phrasing patterns, quantified metrics by function and level.
\subsection{Retrieval}
Hybrid retrieval with query expansion and semantic reranking, bounded by token budgets.
\subsection{Prompt Patterns}
System + instruction + examples + constraints, returning JSON conforming to a schema for deterministic parsing.

\section{Personalization, Recommendations, and Ranking}
\subsection{Signals}
Implicit (clicks, saves) and explicit (thumbs, preferences), plus outcomes (interview, offer) for training.
\subsection{Models}
Contextual bandits or pairwise ranking; cold-start handled via content-based similarity and default priors.
\subsection{Feedback Loops}
User-controlled preference sliders, reranking, and continuous learning.

\section{Frontend Application (Expo/React Native)}
\subsection{Tech Stack}
Expo Router, TypeScript, React Query, Zustand/Redux, secure storage.
\subsection{Screens}
Onboarding, Home/Feed, Job Detail, Tailor, Apply, Tracker, Settings.
\subsection{State and Offline}
Normalized caches, optimistic updates, and offline read for saved jobs and drafts.

\section{Backend Services and APIs}
\subsection{Gateway and Services}
REST/GraphQL gateway; microservices or modular monolith for parsing, scoring, generation, ingestion, and tracking.
\subsection{Auth}
OAuth providers and email/password; token rotation; refresh flows; device-bound secrets.
\subsection{Queues}
Job queues for long-running tasks and backpressure handling.

\section{Data Storage, Caching, and Search}
\subsection{Primary Datastore}
Postgres with JSONB for nested structures; migrations via Prisma/TypeORM.
\subsection{Caching}
Redis for sessions, rate limits, and ephemeral results.
\subsection{Search}
OpenSearch/Meilisearch for text; pgvector/Qdrant for semantic search.

\section{Observability, Telemetry, and Quality Gates}
\subsection{Logging}
Structured, PII-scrubbed logs with correlation IDs.
\subsection{Metrics}
API latency, error rates, model outputs, autofill accuracy, recommendation CTR.
\subsection{Tracing}
Distributed tracing across gateway and services; sampling strategies.
\subsection{Quality Gates}
Automated evaluations for prompts and models; regression guards on key metrics.

\section{Security, Privacy, and Compliance}
\subsection{Privacy by Design}
Data minimization, explicit consent, transparent settings, and export/delete mechanisms.
\subsection{Encryption and Secrets}
TLS in transit; AES-256 at rest; KMS-managed keys; rotation policies; device-bound secure storage.
\subsection{Access Controls}
Role-based access, least privilege, and scoped tokens.
\subsection{Compliance Roadmap}
SOC 2 Type II, GDPR, CCPA readiness with documented controls and evidence collection.

\section{Performance and Scalability Considerations}
\subsection{Scalability}
Horizontal scaling, stateless services, and auto-scaling groups.
\subsection{Resilience}
Rate limiting, backpressure, circuit breakers, and retries with jitter.
\subsection{Latency}
Prompt template pre-warming, caching embeddings, and result reuse.

\section{Accessibility and Internationalization}
\subsection{A11y}
WCAG 2.1 AA semantics, color contrast, focus management, and screen reader support.
\subsection{i18n}
Localization of strings, formats, and job market specifics; RTL readiness.

\section{DevOps, CI/CD, and Environments}
\subsection{Branching and Flags}
Trunk-based development with feature flags and progressive delivery.
\subsection{CI}
Lint, type-check, unit/integration tests, SAST/DAST scans.
\subsection{CD}
Environment-specific configs; blue/green or canary releases; Expo OTA for clients.

\section{Project Plan, Milestones, and Roadmap}
\subsection{Phases}
\begin{enumerate}[leftmargin=2em]
  \item \textbf{Discovery and Design (2 weeks)}: finalize requirements, KPIs, and designs.
  \item \textbf{MVP (8--10 weeks)}: onboarding, discovery, tailoring, apply, tracker.
  \item \textbf{Integrations and Polish (6 weeks)}: ATS connectors, analytics, A11y, i18n.
  \item \textbf{Scale and Compliance (ongoing)}: security hardening, SOC 2 readiness.
\end{enumerate}
\subsection{Milestones}
Design complete; MVP complete; beta launch; GA with first integrations.

\section{Risk Assessment and Mitigation}
\subsection{Top Risks}
\begin{longtable}{p{0.28\linewidth} p{0.64\linewidth}}
\toprule
\textbf{Risk} & \textbf{Mitigation}\\
\midrule
Data privacy incidents & Consent tracking, encryption, secrets hygiene, security reviews.\\
Model hallucinations & Constrained prompting, output validation, human-in-the-loop.\\
Site layout drift & Resilient selectors, synthetic monitoring, rapid mapping updates.\\
Vendor lock-in & Abstraction layers for LLMs, vector stores, and search.\\
\bottomrule
\end{longtable}

\section{Testing Strategy and Validation Plan}
\subsection{Testing Pyramid}
Unit, integration, contract, and end-to-end tests across clients and services.
\subsection{Datasets}
Golden datasets for parsing, skill mapping, and scoring with periodic refresh.
\subsection{Human Review}
Expert curation for generated content; red-teaming for safety and bias.
\subsection{Beta Program}
Opt-in telemetry, privacy filters, and structured feedback channels.

\section{Analytics and Experimentation Framework}
\subsection{Event Schema}
Canonical events for discovery, tailoring, autofill, and submission; privacy filters.
\subsection{Experimentation}
Feature flags, A/B tests on ranking, prompts, and UI variants; guardrail metrics.
\subsection{Outcomes}
Apply rate, interview rate, time saved, CSAT/NPS.

\section{Cost Model and Unit Economics}
\subsection{Cost Drivers}
Model inference, storage, search, ingestion/scraping, observability, and bandwidth.
\subsection{Optimizations}
Prompt caching, batch embeddings, quantization or local inference where feasible.
\subsection{Pricing Hypotheses}
Freemium with Pro tier for resume versions, integrations, and advanced insights.

\section{Future Work and Extensions}
Employer portal with structured shortlists; interview prep copilot; skills gap-to-learning path recommendations with education partners; employer-side analytics and bias checks.

\section{Conclusion and References}
JobEase brings together modern AI and practical automation to reduce friction in job searches and improve outcomes for candidates and employers. By grounding generation in structured data and retrieval, and by designing for privacy and scalability from the outset, JobEase aims to deliver measurable value quickly and responsibly.

\subsection*{References}
\begin{itemize}[leftmargin=2em]
  \item ESCO/ONET skills taxonomies.
  \item ATS best practices and public documentation.
  \item Research on layout-aware document models and retrieval-augmented generation.
\end{itemize}

\appendix
\section*{Appendices}
\addcontentsline{toc}{section}{Appendices}

\section{Glossary}
\begin{description}
  \item[ATS] Applicant Tracking System.
  \item[RAG] Retrieval Augmented Generation.
  \item[PII] Personally Identifiable Information.
\end{description}

\section{API Surface (Illustrative)}
\begin{longtable}{p{0.3\linewidth} p{0.6\linewidth}}
\toprule
\textbf{Endpoint} & \textbf{Description}\\
\midrule
GET /jobs & List and search jobs.\\
POST /applications & Create or submit an application.\\
POST /tailor & Generate tailored resume/cover letter.\\
POST /generate/cover-letter & Create role-specific cover letter.\\
GET /tracker & Retrieve application statuses.\\
\bottomrule
\end{longtable}

\section{Data Contracts (Illustrative)}
CandidateProfile, JobPosting, Application, Recommendation, Insight with typed fields and validation rules.

\section{Prompt Template Skeletons (Illustrative)}
System role and tone; instruction; few-shot examples; output JSON schema.

\section{Security Controls Checklist (MVP)}
Consent recording, encryption at rest and in transit, key rotation, audit logging, access reviews.

\section{Evaluation Rubrics}
Tailoring quality, autofill accuracy, recommendation CTR, safety checks; thresholds and reviewer guidance.

\section{Detailed API Specification}
\subsection{Conventions}
Base URL, versioning strategy (e.g., \texttt{/v1}), authentication via bearer tokens, idempotency keys for POST where applicable, pagination (\texttt{limit}, \texttt{cursor}). Content types: \texttt{application/json}. Responses include \texttt{requestId} and timestamps.
\subsection{Endpoints}
\subsubsection{GET /v1/jobs}
\textbf{Query Params}: \texttt{q}, \texttt{location}, \texttt{remote}, \texttt{seniority}, \texttt{cursor}, \texttt{limit}.
\par\noindent\textbf{Response}
\begin{lstlisting}[style=code]
{
  "requestId": "9b2...",
  "items": [
    {
      "id": "job_123",
      "title": "Frontend Engineer",
      "company": "Acme",
      "location": "Remote",
      "seniority": "Mid",
      "skillsExtracted": ["React", "TypeScript", "CI/CD"],
      "postedAt": "2025-08-01T12:00:00Z"
    }
  ],
  "nextCursor": "abc..."
}
\end{lstlisting}
\subsubsection{POST /v1/tailor}
\textbf{Body}
\begin{lstlisting}[style=code]
{
  "resumeDocumentId": "doc_789",
  "jobId": "job_123",
  "constraints": { "maxPages": 2, "tone": "professional" }
}
\end{lstlisting}
\textbf{Response}
\begin{lstlisting}[style=code]
{
  "requestId": "e51...",
  "tailoredResumeId": "res_456",
  "matchScore": 0.82,
  "changeLog": [{"section": "Experience", "ops": 5}]
}
\end{lstlisting}
\subsubsection{POST /v1/applications}
Creates an application record with status \texttt{draft} or \texttt{submitted}. Includes autofill payload snapshot and validation report.

\section{Algorithms and Methods}
\subsection{Semantic Matching}
\subsubsection{Hybrid Retrieval}
Combine BM25 lexical scores with cosine similarity over embeddings. Final score \(S = \alpha S_{bm25} + (1-\alpha) S_{cos}\), with \(\alpha\) calibrated via offline evaluation.
\subsubsection{Pseudocode}
\begin{lstlisting}[style=code]
function rankJobs(candidateProfile, jobs):
  q_lex = buildLexQuery(candidateProfile.skills, titles, seniority)
  q_vec = embed(candidateProfile.summary)
  C = bm25.search(q_lex, jobs)
  V = vector.search(q_vec, jobs)
  for job in jobs:
    job.score = alpha*C[job].score + (1-alpha)*V[job].cosine
  return sortDescending(jobs, key=score)
\end{lstlisting}
\subsection{Resume Tailoring Heuristics}
Constraint satisfaction to enforce page limits, section ordering, and keyword coverage while preserving factuality. Use greedy selection with backtracking for bullet inclusion under length constraints.
\subsection{Autofill Field Mapping}
Schema alignment via learned sequence labeling over field labels and DOM context with rule-based fallbacks and confidence thresholds.

\section{Data Protection Impact Assessment (DPIA)}
\subsection{Processing Activities}
Parsing resumes, storing candidate profiles, generating tailored content, tracking application statuses, and logging interactions for personalization.
\subsection{Data Categories}
PII (name, contact), employment history, education, skills, optional sensitive inferences (explicitly disabled by default). No special-category data processed without explicit consent.
\subsection{Legal Basis}
Consent for processing candidate data and personalization; legitimate interest for essential telemetry. Contracts for third-party processors.
\subsection{Risk Analysis}
\begin{longtable}{p{0.28\linewidth} p{0.64\linewidth}}
\toprule
\textbf{Scenario} & \textbf{Mitigations}\\
\midrule
Unauthorized access & Access controls, MFA, short-lived tokens, least privilege, audits.\\
Data leakage via logs & PII redaction, log sampling, secure sinks, retention limits.\\
Model memorization & Prompt filtering, output scanning, no raw PII in training corpora.\\
\bottomrule
\end{longtable}
\subsection{Residual Risk and Review}
Residual risk deemed low-to-medium post-controls; semiannual DPIA reviews and breach drills.

\section{Threat Model (STRIDE)}
\begin{longtable}{p{0.18\linewidth} p{0.74\linewidth}}
\toprule
\textbf{Class} & \textbf{Examples and Controls}\\
\midrule
Spoofing & OAuth with PKCE, device-bound tokens, mTLS between services.\\
Tampering & Signed artifacts, checksums for documents, WORM logs.\\
Repudiation & Immutable audit logs, user-visible activity history.\\
Information Disclosure & Field-level encryption, DLP scans, scoped exports.\\
Denial of Service & Rate limits, WAF, autoscaling, circuit breakers.\\
Elevation of Privilege & RBAC, ABAC for sensitive ops, mandatory code reviews.\\
\bottomrule
\end{longtable}

\section{Compliance Mapping}
\subsection{GDPR}
\begin{longtable}{p{0.24\linewidth} p{0.68\linewidth}}
\toprule
\textbf{Article} & \textbf{Implementation}\\
\midrule
Art. 5 (Principles) & Data minimization, purpose limitation, retention controls.\\
Art. 6 (Lawfulness) & Consent flows and records; contract clauses for processors.\\
Art. 15--22 (Rights) & Export, delete, rectify endpoints; DSAR playbook.\\
Art. 32 (Security) & Encryption, access controls, incident response runbook.\\
\bottomrule
\end{longtable}
\subsection{SOC 2 Trust Services}
Security, Availability, Confidentiality mapped to controls: change management, backups, DR, monitoring, and vulnerability management.

\section{Experimentation and Evaluation}
\subsection{Offline Metrics}
Precision@k, nDCG for recommendations; F1 for parsing; ROUGE/BLEU + human ratings for generation quality.
\subsection{Online Experiments}
Randomized controlled trials with guardrails (latency, error rate, safety). Sequential testing to limit exposure.
\subsection{Rubrics}
Detailed checklists for tailoring factuality, style adherence, keyword coverage, and readability.

\section{Cost Model}
\subsection{Unit Costs}
\begin{longtable}{p{0.34\linewidth} p{0.18\linewidth} p{0.36\linewidth}}
\toprule
\textbf{Component} & \textbf{Unit} & \textbf{Notes}\\
\midrule
Embedding inference & per 1K tokens & Batch and cache to reduce repeats.\\
LLM generation & per 1K tokens & Prompt compression and structured outputs.\\
Search index & per GB-month & Lifecycle policies for cold storage.\\
\bottomrule
\end{longtable}
\subsection{Optimization Levers}
Prompt caching, deduplication, approximate nearest neighbor parameters, and mixed-precision inference.

\section{Operations and SRE}
\subsection{SLOs and SLIs}
Availability \(\geq 99.9\%\), API latency P95 \(\leq 500\,ms\), error budget policies, and on-call rotations.
\subsection{Runbooks}
Incident response templates, rollback procedures, and dependency outage playbooks.
\subsection{Backups and DR}
Daily encrypted backups, 30-day retention, quarterly restore tests; RPO 24h, RTO 4h.

\section{Accessibility Audit Checklist}
\begin{longtable}{p{0.64\linewidth} p{0.22\linewidth}}
\toprule
\textbf{Criterion} & \textbf{Status}\\
\midrule
Color contrast \(\geq 4.5:1\) & Planned\\
Keyboard navigation for all flows & Planned\\
Labels and roles for controls & Planned\\
Screen reader announcements & Planned\\
\bottomrule
\end{longtable}

\section{Internationalization Details}
Locales prioritized: en-US, en-GB, hi-IN. Date/number formats, currency, job-market terminology, and RTL readiness.

\section{Project Governance}
\subsection{RACI Matrix}
\begin{longtable}{p{0.28\linewidth} p{0.12\linewidth} p{0.12\linewidth} p{0.12\linewidth} p{0.12\linewidth}}
\toprule
\textbf{Workstream} & \textbf{R} & \textbf{A} & \textbf{C} & \textbf{I}\\
\midrule
Architecture & Lead Eng & CTO & Backend, Mobile & Stakeholders\\
Security/Privacy & Sec Eng & CISO & Legal & All\\
ML/NLP & ML Lead & CTO & Product & Stakeholders\\
\bottomrule
\end{longtable}
\subsection{Timeline Overview}
High-level milestones with dependencies; critical path includes parsing, tailoring, and autofill integrations.

\section{Extended Test Plan}
\subsection{End-to-End Scenarios}
Onboard \(\rightarrow\) discover \(\rightarrow\) tailor \(\rightarrow\) apply \(\rightarrow\) track, with assertions on accuracy and latency at each step.
\subsection{Edge Cases}
Sparse resumes, non-English content, unconventional job descriptions, and long multi-step applications.

\section{Extended Glossary}
\begin{description}
  \item[BM25] A probabilistic retrieval function used in text search.
  \item[nDCG] Normalized Discounted Cumulative Gain for ranking evaluation.
  \item[RBAC/ABAC] Role-/Attribute-based access control models.
\end{description}

\end{document}
